### 2020-06-23 magic_paper.tex
minor changes

The most fundamental and commonly used magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
\end{equation}
It is a monotone function of the $\ell_1$-norm of the Wigner distribution that satisfies the additivity condition.
In particular, mana can be re-expressed as $\mana{\rho} = \log{(2\sn{\rho}+1)}$, where the sum-negativity ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
	\sn{\rho} = \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}

>>>>

The most fundamental and commonly used magic monotone is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \log{\left(\sum\limits_{\bmz \in \pd} \abs{\W[\bmz]{\rho}}\right)}.
\end{equation}
It is a monotone function of the $\ell_1$-norm of the Wigner distribution that satisfies the additivity condition.
In particular, mana can be re-expressed as $\mana{\rho} = \log{(2\hspace{2pt}\sn{\rho}+1)}$, where the sum-negativity ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
	\sn{\rho} = \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}
